---
title: "StockPortfolio Simulation"
author: "Bobby Fatemi"
date: "March 27, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Summary###
This script will optimize a portfolio based on stocks the user provides and the fundemental theory of Portfolio Optimization (Markowitz Mean-Variance Optimization) to derive a portfolio that lands on the efficient frontier (best portfolio given a selection of stocks). Next we will calculate historical returns (**mu**) and risk (**sigma**) of our portfolio and conduct a simulation of random walks (by day, for a year) N times. 

###In Steps###

**STEP 1:** Get historical stock returns and average return (mu) and risk (sigma)

**STEP 2:** Calculate the weights of each stock in a optimal portfolio (efficient frontier)\n

**STEP 3:** Calculate a *portfolio* risk and return pair *(mu, sigma)*

**STEP 4:** Using (mu, sigma) conduct *N* random walks (1 step = 1 day) and average by day across all N random walks

**STEP 5:** Randomly sample another (mu, sigma) from a normal distribution and do STEP 4 again, *M times*

**STEP 6:** Calculate various probabilities from our portfolio simulation

###Historical Average Risk-Returns for Each Stock###
We will use the package `StockPortfolio` for a number of critical steps. Additionally, for our data wrangling and charting needs, we will use `data.table` and `googleVis`, respectively. For this, its also a good idea to turn off scientific notation for presentation of numbers.

```{r, echo=FALSE}
library(stockPortfolio)
library(data.table)
library(googleVis)
options(scipen = 10000)
```

##### Define Stock Tickers and Get Returns #####
Lets say we'd like a technology and banking heavy portfolio. Just because I'm lazy, let's also say we don't care about diversification and we'd like returns calculated on a daily basis going back 5 years: 

```{r,cache=TRUE}
tickers <- c("MSFT", "C", "BAC")
freq    <- "day"
start   <- Sys.Date()-365*5

stockReturns <- getReturns(tickers, freq, start = start)
```
After feeding these inputs to the function `getReturns` from the package `StockPortfolio`, we can see that we get an object of class stockModel, which is really just a list. Let's explore it:

```{r}
stockReturns
names(stockReturns)
lapply(stockReturns[["full"]],head)
```
###Weighting each Stock to get Optimal Portfolio###
Here's where we will gloss over nobel prize winning math, critical explanations of the theory, and anything else that's not cool. Using

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
